---
title: "R Notebook"
output: html_notebook
---


```{r}
data = read.csv('data_est.csv', sep =';')
data
```
Ex1 - Case 3
```{r}
diamonds = na.omit(data$diamonds)
#a)
#population - all diamonds produced by factory
#sample - 12 diamonds selected
#measurement - weight
#b)
n = length(diamonds)
M = mean(diamonds)
S2 = var(diamonds)
S = sd(diamonds)
print(c("mean", "variance", "std"))
print(c(M,S2,S))
alpha = 0.05

conf_int = function(M,S,n, alpha){
  c(M-qt(1-alpha/2, n-1)*S/sqrt(n), M +qt(1-alpha/2,n-1)*S/sqrt(n))
}
print("Confidence Interval: ")
conf_int(M,S,n,alpha)
#d
print("Confidence interval:")
conf_int(M,S,n, 0.01)
print("Confidence interval is wider!!")

#e
print("Confidence Interval variance:")
interval = sigma.test(diamonds, conf.level =1-alpha)$conf.int
print(interval)

#TODO std conf level
```
Ex2 -case 3
```{r}
milk = na.omit(data$milk)
#a
#populationall nursing mothers
#sample 20 women
#mesurement - PCB
#b & c
n = length(milk)
M = mean(milk)
S2 = var(milk)
S = sd(milk)
print(c(M,S2,S))
#d
alpha = 0.05
t.test(milk, conf.level = 1-alpha)$conf.int
#e
interval = sigma.test(milk, conf.level = 1-alpha)$conf.int
print(interval)
#TODO sd
```

Ex3 
```{r}
cigarettes = na.omit(data$cigarettes)

#a
alpha = 0.05
z.test(cigarettes, sigma.x = 0.7, conf.level = 1-alpha)$conf.int
#b
#n>= (z*sigma*2/3)^2
(qnorm(1-alpha/2)*0.7*2/0.3)^2
```

Ex4
```{r}
signal = na.omit(data$signal)

sigma = 3
n = length(signal)
M = mean(signal)
alpha = 0.05
M
z.test(signal, sigma.x = sigma, conf.level = 1 -alpha)$conf.int
```
Ex.5.
```{r}
n=1200
M=4.7
S=2.2
alpha = 0.05

myInterval = function(n,M,S,alpha){
  span = qnorm(1-alpha/2)*S/sqrt(n)
  c(M-span,M+span)
}

myInterval(n,M,S,alpha)
zsum.test(M,S,n, conf.level = 1-alpha)$conf.int
```

Ex.6.
```{r}
lifetime = na.omit(data$lifetime)
alpha = 0.05
n=length(lifetime)
zsum.test(mean(lifetime), sd(lifetime),n, conf.level = 1-alpha)$conf.int
```

Ex.7.
```{r}
#variance 25h^2
S = 5
alpha = 0.05
total_length = 1
(qnorm(1-alpha/2)*S/total_length)^2
```

Ex.8.
```{r}
S = 0.3
alpha = 0.1
total_length = 0.1

(qnorm(1-alpha/2)*S/total_length)^2
(qnorm(1-0.01/2)*S/total_length)^2
```
Ex.9.
```{r}
n = 100
k = 3
T = 3
alpha = 0.05
binom.test(T,n, conf.level = 1-alpha )$conf.int
```

Ex.10.
```{r}
#if p is 0.015 or greater
n=100
T=4
alpha = 0.05
binom.test(T,n, conf.level = 1-alpha )$conf.int
```

Ex.11.
```{r}
n = 120
T = 24
alpha = 0.1
binom.test(T,n, conf.level = 1-alpha)$conf.int
```
Ex.12
```{r}
n=1000
T=122
alpha = 0.1
binom.test(T,n, conf.level = 1-alpha)$conf.int
```
Ex.13
```{r}
alpha =0.02
total_length=0.05
p = 0.5

(qnorm(1-alpha/2)*sqrt((1-p)*p)/ total_length)^2

p=0.3
(qnorm(1-alpha/2)*sqrt((1-p)*p)/ total_length)^2
```

Additional
```{r}
n=5000
T =30
alpha=0.05
phat = T/n

left_inter = max(0,phat - qnorm(1-alpha/2)*sqrt(phat*(1-phat)/n))
right_inter = min(1,phat + qnorm(1-alpha/2)*sqrt(phat*(1-phat)/n))
c(left_inter,right_inter)

binom.test(T,n, conf.level = 1-alpha)$conf.int
prop.test(T,n)$conf.int
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
